### 2013-09-03 pystruct/paper.tex
proof reading of pystruct

\section{Basic Concepts in Structured Prediction}

@@

\subsection{Factor Graphs and the Relation to Graphical Models}
% one factor graph per instance?
In the case when $y$ is multivariate, a very general and widely used method to
specify the structure of a model, and therefore $\Phi$, is using \emph{factor
graphs}. A factor graph is a bipartite graph $(\mathcal{V}, \mathcal{F},
\mathcal{E})$, consisting of variable nodes $\mathcal{V}$, factor nodes
$\mathcal{F}$ and edges $\mathcal{E}$ connecting variables to factors. The
\emph{scope} $N_F$ of a factor $F \in \mathcal{F}$ is defined as
\begin{equation}
    N_F = \{ v \in \mathcal{V} \,|\, (v,F) \in \mathcal{E} \}
\end{equation}
The variable nodes of the factor graph correspond to the entries of the
variables $y$, that is $\mathcal{V} = \{1, \dotsc, n\}$, and each factor node
is associated with a \emph{factor} or \emph{potential function} $\psi_F$.
A factor graph represents a function\footnote{Traditionally factor graphs
 represent \emph{products} of factors.  To simplify presentation, we work
directly in the log-domain of the product representation.}
\begin{equation}\eqlabel{log_factor_graph}
    g(x, y) = \sum_{F \in \mathcal{F}} \psi_F(x, y_{N_F})
\end{equation}
Here, $y_{N_F}$ denotes the entries of $y$ indexed by $N_F$.

@@

\section{Casting Structured Prediction into Software}\label{sec:api}
Unfortunately only few implementations are publicly
available---many applications are based on the non-free implementation
of~\citet{joachims2009cutting}.
Our implementation, \pystruct, aims at providing a high-quality implementation
with an easy-to-use interface, in the high-level Python language.  This allows
practitioners to efficiently test a range of models, as well as allowing
researchers to compare to baseline methods much more easily than this is
possible with current implementations.  \pystruct is BSD-licensed, allowing
modification and redistribution of the code, as well as use in commercial
applications.  By embracing paradigms established in the scientific Python
community and reusing the interface of the widely-used {\sc scikit-learn}
library~\citep{pedregosa2011scikit}, \pystruct can be used in existing
projects, replacing standard classifiers.  The online documentation and
examples help new users understand the somewhat abstract ideas behind
structured prediction.

Using the above formulation, learning can be broken down into three sub-problems:
\begin{enumerate*}
    \item Optimizing the objective with respect to $\theta$.
    \item Encoding the structure of the problem in a joint feature function $\Phi$.
    \item Solving the maximization problem in Equation~\ref{eq:main_equation}.
\end{enumerate*}
The later two problems are usually tightly coupled, as the maximization in
Equation~\ref{eq:main_equation} is usually only feasible by exploiting the
structure of $\Phi$, while the first one is usually treated as independent.
\pystruct takes an object-oriented approach to decouple the task-dependent
implementation of 2. and 3. from the general algorithms used to solve 1.

Estimating $\theta$ is done in \texttt{learner} classes, which currently
support cutting plane algorithms for structural support vector
machines~(SSVMs), subgradient methods for SSVMs, the structured perceptron and
latent variable SSVMs. The cutting plane implementation uses the {\sc cvxopt}
package \citep{dahl2006cvxopt} for quadratic optimization.

@@

\paragraph{Completeness}\pystruct aims at providing full pipelines that can be
    used in applications. It contains model formulation for many typical
    applications.  This is in contrast to \svmstruct that provides no
    models at all, requiring the user to develop significant amounts of code, even
    for simple tasks.

\paragraph{Modularity} \pystruct separates the algorithms of parameter estimation and
     inference from the task-dependent formulation of $\Phi$. This allows
     practitioners, for example in computer vision or natural language
     processing, to improve their model without changing any optimization
     code. On the other hand, researchers working on better inference or
     parameter learning can easily benchmark their improvements on a wide
     array of applications.

\paragraph{Efficiency}
     While \pystruct focuses on usability, providing efficient and competative
     implementations is important to allow fast prototyping and scaling to
     large datasets.

@@

Conditional random fields are an important tool for semantic image
segmentation.  We demonstrate how to learn an $n$-slack support
vector machine on a superpixel-based CRF on the popular Pascal dataset. We use
unary potentials generated using TextonBoost
from \citet{krahenbuhl2012efficient}. The superpixels are generated using SLIC~\citep{achanta2012slic}.%
\footnote{The preprocessed data can be downloaded at \url{http://www.ais.uni-bonn.de/download/datasets.html}.}
Each sample (corresponding on one entry of the list \texttt{X}) is represented as a
tuple consisting of input features and a graph representation.
\begin{listing}[t]
\begin{pythoncode}
model = crfs.EdgeFeatureGraphCRF(
            class_weight=inverse_frequency,
            symmetric_edge_features=[0, 1],
            antisymmetric_edge_features=[2],
            inference_method='qpbo')

@@

\begin{figure}
\centering
\includegraphics[width=.45\textwidth]{times_MNIST}
\includegraphics[width=.45\textwidth]{accs_MNIST}
\caption{Runtime comparison of \pystruct and \svmstruct for multi-class
    classification.
}
\label{fig:timings}
\end{figure}

@@

\section{Summary}
%TODO summarize structured prediction
This chapter introduced \pystruct, a modular structured learning and prediction library in Python.
\pystruct is geared towards ease of use, while providing efficient implementations.
\pystruct integrates itself into the scientific Python eco-system, making it easy to use with
existing libraries and applications.
Currently, \pystruct focuses on max-margin and perceptron-based approaches. In the future,
we plan to integrate other paradigms, such as sampling-based learning~\citep{wick2011samplerank},
surrogate objectives (for example pseudo-likelihood), and approaches that allow for a better integration
of inference and learning~\citep{meshi2010learning}.

>>>>

\section{Basic Concepts in Structured Prediction}\seclabel{basics_structured_prediction}

@@

\subsection{Factor Graphs and the Relation to Graphical Models}\seclabel{factor_graphs}
% one factor graph per instance?
In the case when $y$ is multivariate, a very general and widely used method to
specify the structure of a model, and therefore $\Phi$, is using \emph{factor
graphs}. A factor graph is a bipartite graph $(\mathcal{V}, \mathcal{F},
\mathcal{E})$, consisting of variable nodes $\mathcal{V}$, factor nodes
$\mathcal{F}$ and edges $\mathcal{E}$ connecting variables to factors. The
\emph{scope} $N_F$ of a factor $F \in \mathcal{F}$ is defined as
\begin{equation}
    N_F = \{ v \in \mathcal{V} \,|\, (v,F) \in \mathcal{E} \}
\end{equation}
The variable nodes of the factor graph correspond to the entries of the
variables $y$, that is $\mathcal{V} = \{1, \dotsc, n\}$, and each factor node
is associated with a \emph{factor} or \emph{potential function} $\psi_F$.
A factor graph represents a function\footnote{Traditionally factor graphs
 represent \emph{products} of factors.  To simplify presentation, we work
directly in the log-domain of the product representation.}
\begin{equation}\eqlabel{log_factor_graph}
    g(x, y) = \sum_{F \in \mathcal{F}} \psi_F(x, y_{N_F})
\end{equation}
Here, $y_{N_F}$ denotes the entries of $y$ indexed by $N_F$.

@@

\section{Casting Structured Prediction into Software}\label{sec:api}

Unfortunately only few implementations are publicly
available---many applications are based on the non-free implementation
of~\citet{joachims2009cutting}.
We provide an implementation, \pystruct, which aims at providing a high-quality
code with an easy-to-use interface, in the high-level Python language.  This
allows practitioners to efficiently test a range of models, as well as allowing
researchers to compare to baseline methods much more easily than this is
possible with current implementations.  \pystruct is BSD-licensed, allowing
modification and redistribution of the code, as well as use in commercial
applications.  By embracing paradigms established in the scientific Python
community and reusing the interface of the widely-used {\sc scikit-learn}
library~\citep{pedregosa2011scikit}, \pystruct can be used in existing
projects, replacing standard classifiers. The online documentation and
examples help new users understand the somewhat abstract ideas behind
structured prediction.
We will base the experiments in the rest of this work on the algorithms
implemented in \pystruct.

Using the formulation of structured prediction introduced in
\Secref{basics_structured_prediction}, learning can be broken down into three
sub-problems:
\begin{enumerate*}
    \item Encoding the structure of the problem in a joint feature function $\Phi$.
    \item Solving the loss-augmented prediction problem in Equation~\eqref{loss_augmentation}.
    \item Optimizing the objective \Eqref{learning_equation} with respect to $\theta$.
\end{enumerate*}
The first two problems are usually tightly coupled, as the maximization in
Equation~\ref{eq:main_equation} is usually only feasible by exploiting the
structure of $\Phi$, as described in \Secref{factor_graphs}. The last problem,
finding $\theta$, on the other hand, is usually treated as independent.
\pystruct takes an object-oriented approach to decouple the task-dependent
implementation of 2. and 3. from the general algorithms used to solve 1.

Estimating $\theta$ is done in \texttt{learner} classes, which currently
support cutting plane algorithms for structural support vector
machines~(SSVMs), the Block-Coordinate Frank Wolfe (BCFW) algorithm for SSVMs,
subgradient methods for SSVMs, the structured perceptron and latent variable
SSVMs. The cutting plane implementation uses the {\sc cvxopt}
package \citep{dahl2006cvxopt} for quadratic optimization.

@@

\paragraph{Completeness}
    \pystruct aims at providing complete predictors that can be used directly in
    applications. It contains model formulation for many typical scenarios.
    This is in contrast to \svmstruct that provides no models at all, requiring the
    user to develop significant amounts of code, even for simple tasks.

\paragraph{Modularity}
    \pystruct separates the algorithms for parameter estimation and
     inference from the task-dependent formulation of $\Phi$. This allows
     practitioners, for example in computer vision or natural language
     processing, to improve their model without changing any optimization
     code. On the other hand, researchers working on better inference or
     parameter learning can easily benchmark their improvements on a wide
     array of applications.

\paragraph{Efficiency}
     While \pystruct focuses on usability, providing efficient and competative
     implementations is important to allow fast prototyping and scaling to
     large datasets. \pystruct achieves the same runtime performance
     as the popular \svmstruct model for cutting plane algorithms, and
     provides implementations of the BCFW and Subgradient methods that scale to
     large datasets.

@@

We demonstrate the use of \pystruct on the task of semantic image segmentation,
the main focus of this work. The example shows how to learn an $n$-slack support
vector machine on a superpixel-based CRF on the popular Pascal dataset. We use
unary potentials generated using TextonBoost
from \citet{krahenbuhl2012efficient}. The superpixels are generated using SLIC~\citep{achanta2012slic}.%
\footnote{The preprocessed data can be downloaded at \url{http://www.ais.uni-bonn.de/download/datasets.html}.}
Each sample (corresponding on one entry of the list \texttt{X}) is represented as a
tuple consisting of input features and a graph representation.
\begin{listing}[t]
\begin{pythoncode}
model = crfs.EdgeFeatureGraphCRF(
            class_weight=inverse_frequency,
            symmetric_edge_features=[0, 1],
            antisymmetric_edge_features=[2],
            inference_method='qpbo')

@@

\begin{figure}
\centering
\includegraphics[width=.49\textwidth]{times_MNIST}
\includegraphics[width=.49\textwidth]{accs_MNIST}
\caption{Runtime comparison of \pystruct and \svmstruct for multi-class
    classification.
}
\label{fig:timings}
\end{figure}

@@

\section{Summary}
Im this chapter, we introduced basic concepts of structured prediction. In particular, we discussed
Structured Support Vector Machines, a max-margin approach for training linear predictors for
structured data. %TODO comparison of algorithms?
We gave a description of several popular learning algorithms, together with their theoretical
runtime bounds and practical considerations.
%TODO summarize structured prediction
We also introduced \pystruct, our modular structured learning and prediction library in Python.
\pystruct is geared towards ease of use, while providing efficient implementations and will be the
basis of our further experiments.
\pystruct integrates itself into the scientific Python eco-system, making it easy to use with
existing libraries and applications.
Currently, \pystruct focuses on max-margin and perceptron-based approaches.
In the future, we plan to integrate other paradigms, such as sampling-based
learning~\citep{wick2011samplerank}, surrogate objectives (for example
pseudo-likelihood), and approaches that allow for a better integration of
inference and learning~\citep{meshi2010learning}.
